Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
modify Ad-ii to include 3s

\todo{Peter:I'm still kind of unhappy with the notation $y_{e_i'}$ because it is treating $e_i'$ like a formal object rather than a number. What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$}
\begin{enumerate}
	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i, e_i'})
		= \frac{e_i'- 1}{2}$.
	\item[(Ad-ii)] Any generator $z \neq y_{i, e_i'}$
		of $R'$ satisfies
		\begin{align*}
			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] The minimality condition
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

@@

Finally, to check (e), we will first show that $(\sx,J)$ is
admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
strictly monotonic in the $e_i$, and hence also holds for $(\sx,J)$.
Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by
definition. This is where we use that (Ad-iii) holds for $d > 0$
and not just for $d = 0$.

Finally, if $(\sx , J)$ is admissible then so is $(\sx,W)$ for any
$W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
\end{proof}

>>>>

\todo{Peter:I'm still kind of unhappy with the notation $y_{e_i'}$ because it is treating $e_i'$ like a formal object rather than a number. What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$}
\begin{enumerate}
	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i, e_i'})
		= \frac{e_i'- 1}{2}$.
	\item[(Ad-ii)] Either $e_j' = 3$ for all $j \in \{1, \ldots, r\}$
		or any generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
		\begin{align*}
			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] The minimality condition
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

@@

Finally, to check (e), we will first show that $(\sx,J)$ is
admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
strictly monotonic in the $e_i$ and hence also holds for $(\sx,J)$.
Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by
definition. This is where we use that (Ad-iii) holds for $d > 0$
and not just for $d = 0$.

Finally, if $(\sx , J)$ is admissible then so is $(\sx, W)$ for any
$W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
\end{proof}
